\documentclass[overlapped,12pt]{res}

\usepackage[
  top=6.5em,
  bottom=3em,
  left=5.5em,
  right=8.5em,
]{geometry}

\begin{document}

%-------------------------------------------------------------------------------
%	RES.CLS CUSTOMISATIONS
%-------------------------------------------------------------------------------
% remove horizontal lines
\renewcommand{\fullline}{}

% add a 0.1em space between position title section and body section
\makeatletter
\renewenvironment{position}
  {
   \begingroup
     \par
       \the\tabular@head
     \penalty -\@secpenalty
     \penalty 10000
     \ignorespaces
     \\[-0.9em]
  }{
       \the\tabular@tail
     \penalty \@secpenalty
    \endgroup
}
\makeatother

% used for linebreaks within sections
\newcommand{\tinylinebreak}{\\\\[-0.9em]}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{{\Huge Conor Taylor}}

\address{
  Folkskolegatan 22C\\
  11735 Stockholm\\
  Sweden}
\address{
  \hfill conor@taylor.sh\\
  \hfill (+46) 73 0924109\\
  \hfill taylorconor.com\\
  \hfill github.com/taylorconor}

\begin{resume}

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\employer{l}\title{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}

\section{EXPERIENCE}
\employer{\textbf{Spotify}}
\location{Stockholm, Sweden}
\dates{May 2016 - present}
\title{Senior Software Engineer}
\begin{position}
Java and C++ engineer, working on highly scalable Java backend services with
over 150M active users, along with C++ client development. I work on
architecting, implementing and maintaining lots of critical Spotify features,
including the backend and client for Spotify Connect, the backend for the Web
Player, Spotify for Google Home, Spotify on Sonos, and the Spotify desktop
clients for macOS, Windows and Linux.
\tinylinebreak
Promoted to Senior Software Engineer in June 2018.
\end{position}

\employer{\textbf{Bloomberg}}
\location{London, U.K.}
\dates{May 2015 - August 2015}
\title{Software Engineer Intern}
\begin{position}
Intern backend C++ developer in the Electronic Trade Order Management Systems
team. I worked on a research project focused on reducing latency involved in
high-frequency trade operations for all Bloomberg Terminal traders.
\end{position}

\employer{\textbf{Hunite}}
\location{Amsterdam, Netherlands}
\dates{May 2014 - February 2015}
\title{Software Engineer}
\begin{position}
Airline timetable scheduling software. I worked on the iOS and Android clients,
the site backend and database, and the API used to interface with the rest of
the Hunite ecosystem. I also wrote web scrapers and parsers for data mining
purposes, to extract and interpret complex roster sheets.
\end{position}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Trinity College Dublin}\hfill
Dublin, Ireland\\
{\sl BA (Mod)}, Computer Science, May 2016\hfill 
First Class Honours

%-------------------------------------------------------------------------------
%	SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages}: C++, Java, C, Objective C, Python, PHP.\\
\textbf{Applications}: Git, Docker, GCP.\\
\textbf{Operating Systems}: Linux, macOS, Windows, iOS.

%-------------------------------------------------------------------------------
%	OTHER PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{OTHER PROJECTS}
Speaker at CoDe-conf Copenhagen 2018 (upcoming). code-conf.com/2018/cph.\\
p2psc C++ library for P2P sockets using TCP hole punching.\\
Adaptive load balancing framework for testing load balancing algorithms in
HAProxy.
%-------------------------------------------------------------------------------
\end{resume}
\end{document}
